---
title: "Lab instructions"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
question_rank <- function(..., random_answer_order = TRUE, options = sortable::sortable_options()) {
  learnr::question(
    ...,
    random_answer_order = random_answer_order,
    type = "sortable_rank",
    options = options
  )
}
```


## Om programmet

### Introduktion till Analysvetenskap och Forensik 

*Vad innebär analysvetenskap*
Titta noga igenom nedan video, besvara sedan frågorna för att kunna gå vidare. Fler än ett svar kan finnas.
![](https://www.youtube.com/watch?v=u-0hmQicZco)

### Fråga 1

```{r Q1, echo=FALSE}
question("Vilka är de huvudsakliga ämnen som programmet innefattar",
  answer("Forensik", correct = TRUE),
  answer("Statskunskap"),
  answer("Analytisk kemi och relaterade ämnen", correct = TRUE),
  answer("Kriminologi"),
  random_answer_order = TRUE,
  incorrect = "Fel, försök igen",
  allow_retry = TRUE
)
```

### Fråga 2

```{r Q2, echo=FALSE}

Q2_x <- sample(1:5, 1)

question(sprintf("Hur många enheter går det på $%s$ mol?", Q2_x),
  answer(sprintf("$%e$", Q2_x*6.022e+23), correct = TRUE),
  answer(sprintf("$%e$", Q2_x*6.022e+23/2)),
  answer(sprintf("$%e$", Q2_x*1.32e+10)),
  answer(sprintf("$%e$", Q2_x*3e+5)),
  random_answer_order = TRUE,
  incorrect = "Fel, försök igen",
  allow_retry = TRUE
)

```

### Fråga 3
```{r Q3, echo=FALSE}

question_text("Vad heter programansvarig för analysvetenskapliga programmet i kemi?",
              answer("Than Wan", message = "Nej!"),
              answer("Thanh Wan", message = "Förnamn rätt, efternamn fel, försök igen"),
              answer("Than Wang", message = "Förnamn fel, efternamn rätt!"),
              answer("Thanh Wang", message = "Jaa!", correct = TRUE),
              allow_retry = TRUE,
              options = list(
                placeholder = "Förnamn Efternamn",
                trim = TRUE)
)

```


```{r sortable_question, echo = FALSE}
rank_ex <- sortable::question_rank(
  "Sort the first 5 letters",
  learnr::answer(LETTERS[1:5], correct = TRUE),
  learnr::answer(rev(LETTERS[1:5]), correct = FALSE, "Other direction!"),
  allow_retry = TRUE
)
rank_ex
```


## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

